Fail Faster

### 2025-03-24 paper/paper.tex
two

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
Property-based testing (PBT) relies on generators for random test
cases, often constructed using embedded domain specific languages,
which provide expressive combinators for building and composing
generators.  The effectiveness of PBT depends critically on the speed
of these generators.
%
However, careful measurements show that the generator performance of
two widely used PBT libraries falls well short of what is possible,
due principally to (1) the abstraction overhead of their
combinator-heavy style and (2) suboptimal sources of randomness.
We characterize, quantify, and address these bottlenecks.

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
Property-based testing (PBT) relies on generators for random test
cases, often constructed using embedded domain specific languages,
which provide expressive combinators for building and composing
generators.  The effectiveness of PBT depends critically on the speed
of these generators.
%
However, careful measurements show that the generator performance of
widely used PBT libraries falls well short of what is possible,
due principally to (1) the abstraction overhead of their
combinator-heavy style and (2) suboptimal sources of randomness.
We characterize, quantify, and address these bottlenecks.
